### 2016-02-29 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Updated hose stream/FDS reports, edited drawings & condensed inventor files

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{..//Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
	\caption[Dimensioned floor plans of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_dimensioned_plan}
\end{figure}
% make new 1st floor plan with rear door completely sealed off

@@

\section{Instrumentation}
\label{sec:Instrumentation}
The structures were instrumented for temperature, gas velocity, heat flux, and gas concentration measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample. Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured. A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.

% \begin{figure}[!ht]
% 	\includegraphics[width=0.35\columnwidth]{../Figures/Floor_Plans/Legend}
% 	\caption[Instrumentation Legend.]{Instrumentation Legend.}
% 	\label{fig:Instrumentation_Legend}
% \end{figure}

@@

\subsubsection*{East Structure}
Three different test series -- Series 4, Series 5, and Series 6 -- were conducted in the east structure. Each series was composed of three experiments that used an identical procedure to change the ventilation pattern in the structure. The three procedures used for each test series are outlined in Figs.~\ref{fig:east_test_4}-\ref{fig:east_test_6}.

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & West double door opened \\
 	5 	 & East double door opened \\
 	6	 & South side door opened \\
 	7-9  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Test Series 4 layout and ordered sequence of events.}
\label{fig:east_test_4}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & Roof vent opened \\
 	5 	 & West double door opened \\
 	6 	 & East double door opened \\	
 	7	 & Roof vent closed \\
 	8-10  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test Series 5 layout and ordered sequence of events.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & Roof vent opened \\
 	5 	 & West double door opened \\
 	6-8  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test Series 6 layout and ordered sequence of events.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

\subsubsection*{West Structure}
Two different test series -- Series 22 and Series 24 -- were conducted in the west structure. Each series was composed of two experiments that used an identical procedure to change the ventilation pattern in the structure. The two procedures used for each test series are outlined in Figs.~\ref{fig:west_test_22} and \ref{fig:west_test_24}.

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & 2nd floor west double door opened \\
 	5 	 & 1st floor west double door opened \\
 	6	 & 2nd floor east double door opened \\
 	7 	 & 1st floor east double door opened \\
 	8-10  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	% \includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_Test_22}
\end{minipage}
\caption{Test Series 22 layout and ordered sequence of events.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & Interior stairwell door opened \\
 	5 	 & 1st floor west double door opened \\
 	6	 & 2nd floor west double door opened \\
 	7 	 & 2nd floor south side door opened \\
 	8-10 & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	% \includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_Test_24}
\end{minipage}
\caption{Test Series 24 layout and ordered sequence of events.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

>>>>

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}
[FDS intro, importance of validation, fact this report only includes experimental setup and procedure]

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{..//Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
	\caption[Dimensioned floor plans of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_dimensioned_plan}
\end{figure}

@@

\section{Instrumentation}
\label{sec:Instrumentation}
The structures were instrumented for temperature, gas velocity, heat flux, and gas concentration measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample. Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured. A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics discussed in the follow sections.

\begin{figure}[!ht]
	\includegraphics[width=0.25\columnwidth]{../Figures/Floor_Plans/Instrumentation_Legend}
	\caption{Instrumentation Legend.}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

\subsubsection*{East Structure}
Three different test series---Series 4, Series 5, and Series 6---were conducted in the east structure. Each series was composed of three experiments that used an identical procedure to change the ventilation in the structure. The experiments conducted during Series 4 followed a procedure in which each exterior door was opened to change the ventilation pattern. During the experiments in Test Series 5, each double door was opened and the roof vent was opened and closed throughout the procedure. Both the roof vent and west double door were opened during each experiment in Series 6. Figs.~\ref{fig:east_test_4}--\ref{fig:east_test_6} outline the experimental procedures of Test Series 4--6 in more detail.

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & West double door opened \\
 	5 	 & East double door opened \\
 	6	 & South side door opened \\
 	7-9  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Test Series 4 layout and sequence of events.}
\label{fig:east_test_4}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & Roof vent opened \\
 	5 	 & West double door opened \\
 	6 	 & East double door opened \\	
 	7	 & Roof vent closed \\
 	8-10  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test Series 5 layout and sequence of events.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & Roof vent opened \\
 	5 	 & West double door opened \\
 	6-8  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test Series 6 layout and sequence of events.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

\subsubsection*{West Structure}
Two different test series---Series 22 and Series 24---were conducted in the west structure. Each series was composed of two experiments that used an identical procedure to change the ventilation in the structure. Experiments conducted during Series 22 followed a procedure in which each double door on the first and second floors was opened. Experiments from Series 24 followed a sequence of events that involved opening the interior stairwell door, opening the west double door on both the first and second level, and opening the south side exterior door on the second level of the structure. Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} outline the experimental procedures of Test Series 22 and 24 in more detail.

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & 2nd floor west double door opened \\
 	5 	 & 1st floor west double door opened \\
 	6	 & 2nd floor east double door opened \\
 	7 	 & 1st floor east double door opened \\
 	8-10  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Test Series 22 layout and sequence of events.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & Interior stairwell door opened \\
 	5 	 & 1st floor west double door opened \\
 	6	 & 2nd floor west double door opened \\
 	7 	 & 2nd floor south side door opened \\
 	8-10 & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Test Series 24 layout and sequence of events.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

### 2016-02-29 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated hose stream/FDS reports, edited drawings & condensed inventor files

\chapter{Results and Discussion}
\label{chap:results}
In the following sections, the measurements will be presented in graphic and tabular form. In the graphs, an error bar will represent the estimated uncertainty of the measurement. In the tables, the uncertainty will be included in the caption of the table.

@@

Fig.~\ref{fig:Test_16_A10_Avgs} contains a plot of the average velocity measured by the bi-directional probes at A10 for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16. Similar plots that were generated using measurements obtained from the bi-directional probes at A10 during Test 17 and measurements obtained from the bi-directional probes at A6 during Test 33 are presented in Appendix~\ref{sec:monitor_figs}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
	\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

For every hose stream and target location combination during the monitor experiments, there was always significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established. Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, and 33.

\begin{table}[!ht]
\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \midrule
 & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} \\
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\multicolumn{3}{c}{} 
\\
\midrule
\textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
\\ \multicolumn{6}{c}{} \\
\textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}
\FloatBarrier

**** Discuss tabulated results, main point being fogs move more air than straight ****

@@

Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average velocity measured by the bi-directional probes at A10 for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18. Similar plots that were generated using measurements obtained from the bi-directional probes at A10 during Test 19 and measurements obtained from the bi-directional probes at A6 during Test 34 are presented in Appendix~\ref{sec:handline_figs}.

@@

For every hose stream and application pattern combination tested during the handline experiments, there was always significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established. Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18 and 19, respectively.

@@

Similar to the monitor experiments, there is a significant difference between the average air velocity caused by the fixed straight stream and the average velocity caused by the narrow and wide fog streams; the velocities for the narrow and wide fog were always significantly higher than the velocity of the fixed stream. Additionally, it was only when the hose began to move around that the air velocity through the doorways for the straight stream approached the air velocities associated with the narrow and wide fogs for the corresponding pattern. However, the straight stream hose pattern always resulted in the lowest average air velocity through the doorway for the three different hose streams at each of the four application patterns.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
	\label{fig:Test_33_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier

>>>>

\chapter{Results and Discussion}
\label{chap:results}
In the following sections, the measurements are presented in graphic and tabular form. In the graphs, an error bar will represent the estimated uncertainty of the measurement. In the tables, the uncertainty will be included in the caption of the table.

@@

Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 16. Similar plots of the average measured velocity through the interior doorway for Tests 17, 33, and 70 are presented in Appendix~\ref{sec:monitor_figs}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity through the interior stairwell door (A10) during Test 16 for the three hose stream patterns.}
	\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}

Excluding the straight stream during Test 33, there was significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established for every hose stream and target location combination during the monitor experiments. Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, 33, and 70.

\begin{table}[!ht]
\caption{Average air velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{5}{c}{\large ------------------------ 120 GPM ------------------------} 
\\
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \midrule
 & \multicolumn{2}{c}{\large --- 180 GPM ---} & \multicolumn{3}{c}{} 
\\
 & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} 
\\
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\multicolumn{3}{c}{} 
\\
\midrule
\textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
\\ \multicolumn{6}{c}{} \\
\textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

Looking at Tests 16, 17, and 33 in Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities when the flow path was fully established through the interior doorway compared to the straight stream. This trend is also observed in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} above and Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{sec:monitor_figs}. Additionally, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream. Finally, the Test 70 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_70_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle produce approximately the same amount of air movement through the interior doorway.
\FloatBarrier

@@

Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18. Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{sec:handline_figs}.

@@

Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity through the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18-19, respectively.

@@

Nearly every hose stream and application pattern combination using a narrow or wide fog stream during the handline experiments produced significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established. For the straight stream, however, significant air movement through the interior doorway was only reached once the stream was applied in a pattern that involved moving the handline. Similar to the monitor experiments, the average air velocity through the interior doorway while the flow path was established was always greater in magnitude for the application patterns using the narrow and wide fog streams than the same patterns using the straight stream.

% --- STOPPED --- %

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
	\caption{Average velocity through stairwell door during Test 13 for three hose stream patterns.}
	\label{fig:Test_33_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier
